Strong lensing selection effects

### 2022-08-03 paper/seleff.tex
stuff

%At the brightest flux explored in the experiment (red line in \Fref{fig:extcs}), $\crosssect$ increases with increasing source size, before dropping to zero.
At the brightest flux explored in the experiment (red line in \Fref{fig:extcs}), the lensing cross-section at small source sizes is larger than the area enclosed within the radial caustic (red ellipse in \Fref{fig:ellcaust}).
This is because, when the source is very bright, it can give rise to multiple images even while its centroid lies outside of the radial caustic, as long as its surface brightness distribution extends into it.
This also explains why $\crosssect$ increases with increasing source size, before dropping to zero: the more extended the source, the farther away from the lens centre it can be while still producing multiple images.

>>>>

%At the brightest flux explored in the experiment (red line in \Fref{fig:extcs}), $\crosssect$ increases with increasing source size, before dropping to zero.
At the brightest flux explored in the experiment (green line in \Fref{fig:extcs}), the lensing cross-section at small source sizes is larger than the area enclosed within the radial caustic (black dotted line in \Fref{fig:extcs}).
This is because, when the source is very bright, it can give rise to multiple images even while its centroid lies outside of the radial caustic, as long as its surface brightness distribution extends into it.
This also explains why $\crosssect$ increases with increasing source size, before dropping to zero: the more extended the source, the farther away from the lens centre it can be while still producing multiple images.
